\thispagestyle{plain}

\noindent
\today

\noindent
Visa Section \\
The Canadian Embassy \\
No. 58, Cinnah Street \\
Çankaya 06690, Ankara \\
Turkey \\

Dear Officer,

I am writing to provide my proof of financial capability in support of my Study Permit application for Canada. My name is Alireza Heidari, and I have been accepted into the Master of Science in Computing Science program at Simon Fraser University (SFU), with studies commencing in \textit{January 2025}.

For the first year of my studies, I have secured a total of \textbf{CAD {\totalFunds}}. This amount includes a family contribution of approximately CAD {\sponsorFunds}, which comprises around CAD {\sponsorFunds} held in my mother's account and about CAD {\selfFunds} in my personal account. Additionally, I have been awarded financial support from SFU totaling at least CAD {\universityFunds} per year for two years. This funding includes scholarships, research funds, and teaching assistantships, as outlined in my admission letter. 

I have estimated my first-year expenses to be \textbf{CAD {\totalExpenses}}, which is marginally higher than the official estimates provided by SFU, IRCC, and other reliable sources. After accounting for these expenses, I will have \textbf{CAD {\remainingFunds}} remaining, representing a comfortable margin of \textbf{{\remainingFundsToExpensesPercentage}} above the estimated costs. These available funds will enable me to manage any unforeseen expenses that may arise during my studies in Canada.

I have also secured housing at SFU Residence and Housing from January 2025 to August 2025, with the option to extend for the following year. A deposit has already been paid, as confirmed in the attached documentation.

I have enclosed all relevant financial documentation for your review. Please feel free to contact me if you require any further information or clarification.

Thank you for your time and consideration of my application.

\noindent
Sincerely,\\
Alireza Heidari

\clearpage
