\thispagestyle{plain}

\noindent
\today

\noindent
Visa Section \\
The Canadian Embassy \\
No. 58, Cinnah Street \\
Çankaya 06690, Ankara \\
Turkey \\

Dear Officer,

I am writing to respectfully submit additional information in support of my application for a Study Permit visa. My name is Alireza Heidari, and I have been accepted into the Master of Science in Computing Science program at Simon Fraser University (SFU), with studies commencing in \textit{January 2025}.

This is a full-time, thesis-based MSc program offered by SFU’s Department of Computing Science, with an expected duration of two years. The program requires the completion of five graduate-level courses and an 18-credit thesis, which will culminate in a seminar presentation and formal defense. I am also fortunate to have been awarded a financial package totaling at least CAD \$21,000 per year. This financial support is composed of research grants, teaching assistantships, and scholarships.

% If your admission is conditional, uncomment the following paragraph and fill in the necessary details.
%I understand that my admission is conditional upon SFU receiving my official final transcript from Sharif University of Technology before my second term. I am currently completing my final undergraduate course, which is expected to conclude by December 2024. Upon completion, I will promptly submit my official transcript to fulfill the admission requirement.

I have enclosed all the relevant supporting documents for your reference. Should you require any additional information or clarification, please do not hesitate to contact me.


Thank you for your time and consideration of my application.


\noindent
Sincerely,\\
\docAuthor

\clearpage
